\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-29 OaklandSubmission/intro.tex
nit

\subsubsection*{Cryptogaphic-cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and generates non-cryptographic code for it.\rs{check this}
Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an effcient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Indeed, \tool is the
first such cryptographic-cost aware compiler.

>>>>

\subsubsection*{Cryptogaphic-cost aware compiler} The \tool compiler
compiles a source program to a hybrid computation consisting
of \emph{public} and \emph{secret} parts. In the example above, for
instance, \tool compiler realizes that the array index~\ls{i} is
public, and generates non-cryptographic code for the array accesses.
Further, within the secret parts, \tool compiler is
aware
of the cryptographic costs of arithmetic and boolean representations
of the source language operators. Based on these costs, the compiler
automatically picks arithmetic or boolean
representations for different sub-parts, and generates the
corresponding circuits along with the required inter-conversion
gates. The outcome is an effcient \mpc protocol combining arithmetic
and boolean circuits, while the programmer remains
oblivious of all these cryptographic details. Indeed, \tool is the
first such cryptographic-cost aware compiler.
